For submission to the Journal of Integrated Pest Management

### 2021-06-03 ofv_fife_2021.Rmd
minor edits

OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020]. Mechanical transmission of OFV is possible to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013], under laboratory conditions.

During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv. 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`). *Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, which includes a diverse array of various monocotyledonous southeastern Asia native liliod plants [@Chase2009; @Meng2021]. *Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover nursery plants in the southeastern United States [@Mcharo2003].

>>>>

OFV naturally infects more than fifty species of Orchidaceae [@Kitajima2010; @Peng2013], some Asparagaceae (Nolinoidaea) [@Mei2016; @Dietzgen2018b], and Rutaceae: (*Citrus*), where it causes citrus leprosis-like symptoms [@Cook2019; @OlmedoVelarde2019; @Roy2015; @Roy2020]. Mechanical transmission of OFV is possible under laboratory conditions to some plants belonging to the plant families Chenopodiaceae, Aizoaceae, Fabaceae, and Solanaceae [@Chang1976; @Kondo2003; @Peng2013].

During June 2020, chlorotic ringspot symptoms were observed on Giant Lilyturf *Liriope* spp., cv. 'Gigantea' in a landscape of Leon County, Florida (`r citef("fig_1")`). *Liriope* belong to a group of plants in the family Asparagaceae, subfamily Nolinoidaea, comprised of grass-like monocotyledonous liliod plants native to southeastern Asia [@Chase2009; @Meng2021]. *Liriope* and the closely related *Ophiopogon* Ker Gawler (Asparagaceae: Nolinoidaea) are considered the most important ground cover plant in the southeastern United States [@Mcharo2003].
